detector evaluation

### 2018-01-24 analysis-validation/detector_evaluation.Rmd
wrist eval

>>>>

OPENPOSE WRISTS
```{r}
data <- read_csv("data/final_output/openpose_results_truncated_2.csv") %>%
  distinct(name, frame, .keep_all = TRUE)

data %<>%
  mutate(is_face = ifelse(LWrist_conf != 0 | RWrist_conf != 0, "True", "False"))%>%
  select(group, name, frame, is_face) %>%
  rename(video = name)

ground_truth_data <- read_csv("data/ground_truth/ground_truth_wrists.csv") %>%
  arrange(video, frame) %>%
  cbind(read_csv("data/ground_truth/gold_set_candidates2.csv") %>%
          arrange(video, frame) %>%
          select(sample_type))
```
